### 2016-09-29 rebuttal.tex

\question All ``submodules'' should be replaced by ``modules'' (examples:
lines 657, 662).
\label{rev3point37}
\begin{solution}
  Our use of ``modules'', ``submodules'', and ``packages'' coincides with the
  definitions used in the official Python documentation (see
  \url{https://docs.python.org/3/tutorial/modules.html#packages} and
  \url{https://docs.python.org/3/glossary.html#term-package}). To clarify
  things, we have modified the manuscript to use ``package'' only when
  referring to a library external to SymPy (such as mpmath and Xy-pic).

To avoid confusion, and to be consistent with the definitions used by the
official Python documentation, we have modified the manuscript to use
``submodule'' to refer to any module that is a dotted submodule of
\texttt{sympy}, such as \texttt{sympy.physics.quantum}. This is to emphasize
that these submodules all live within the \texttt{sympy} namespace, as ``module''
can suggest a separate library.
\end{solution}

\question The sentences in lines 657--661 should swap places, because ``areas of mathematics'' are discrete mathematics, concrete mathematics, etc., while simplifying expressions, performing common calculus operations, pretty printing expressions, etc.\ belongs to common operations (``other areas'' is also fine, albeit slightly wrong).
\begin{solution}
The ``areas of mathematics'' was intended to encompass all mathematical
operations. We have rewritten the first sentence as
\begin{quote}
SymPy supports a wide array of mathematical facilities.
\end{quote}
We have also changed ``other included areas'' to ``other supported facilities'' in the third sentence.

The order of the subsequent sentences was chosen to match the order they were
presented in the paper. We have modified them to match the current ordering in
the paper.
\end{solution}

\question In line 662 ``classical mechanics and quantum mechanics'' are listed as the only example of the support for specific domains, as in section 5, which leaves the impression that physics the only one. Either more domains should be listed, or it should be reworded to recognize the fact that there are no others.
\begin{solution}
  We have changed the text to ``certain specific physics domains''. Also, we
  list here only two of the above mentioned submodules in
  \texttt{sympy.physics}, but there are others.
\end{solution}

### 2016-09-29 rebuttal.tex

\question The sentences in lines 657--661 should swap places, because ``areas of mathematics'' are discrete mathematics, concrete mathematics, etc., while simplifying expressions, performing common calculus operations, pretty printing expressions, etc.\ belongs to common operations (``other areas'' is also fine, albeit slightly wrong).
\begin{solution}
The ``areas of mathematics'' was intended to encompass all mathematical
operations. We have rewritten the first sentence as
\begin{quote}
SymPy supports a wide array of mathematical facilities.
\end{quote}
We have also changed ``other included areas'' to ``other supported facilities'' in the third sentence.

The order of the subsequent sentences was chosen to match the order they were
presented in the paper. We have modified them to match the current ordering in
the paper.
\end{solution}

\question In line 662 ``classical mechanics and quantum mechanics'' are listed as the only example of the support for specific domains, as in section 5, which leaves the impression that physics the only one. Either more domains should be listed, or it should be reworded to recognize the fact that there are no others.
\begin{solution}
  We have changed the text to ``certain specific physics domains''. Also, we
  list here only two of the above mentioned submodules in
  \texttt{sympy.physics}, but there are others.
\end{solution}

\question Lines 670--678 contain explanations what some of the authors' institutions are. It is customary to use acknowledgements to thank people and institutions, while institutions' details should be provided in the authors' footnotes in the documents' head.
\begin{solution}
  The institution details were moved to the footnotes in the head of the
  paper. The acknowledgments section was removed, as per the PeerJ staff
  requested technical changes (this information is to be listed separately as
  a funding statement deceleration as part of the submission process).
\end{solution}

### 2016-09-29 gruntz.tex
Remove spaces around em dashes
Cross reference gruntz footnote in rebuttal

The Gruntz algorithm is now illustrated with the following example:
\begin{equation}
    \label{gruntz_example_fn}
f(x) = e^{x+2e^{-x}} - e^x + {1\over x} \,.
\end{equation}
First, the set of most rapidly varying subexpressions is determined ---
the so-called \textit{mrv set}. For~\eqref{gruntz_example_fn}, the mrv set
$\{e^x, e^{-x}, e^{x+2e^{-x}}\}$ is obtained. These are all subexpressions of%
~\eqref{gruntz_example_fn} and they all belong to the same comparability
class. This calculation can be done using SymPy as follows:

@@

In this example the result ($2+{1\over x}$) still depends on $x$, so the above procedure is
repeated until just a value independent of $x$ is obtained. This is the final
limit. In the above case the limit is $2$, as can be
verified by SymPy\footnote{To see intermediate steps, discussed above, interested
reader can switch on debugging output by setting
\texttt{SYMPY\_DEBUG} environment variable, before importing anything from
the SymPy namespace.}:

>>>>

The Gruntz algorithm is now illustrated with the following example:
\begin{equation}
    \label{gruntz_example_fn}
f(x) = e^{x+2e^{-x}} - e^x + {1\over x} \,.
\end{equation}
First, the set of most rapidly varying subexpressions is determined---the
so-called \textit{mrv set}. For~\eqref{gruntz_example_fn}, the mrv set
$\{e^x, e^{-x}, e^{x+2e^{-x}}\}$ is obtained. These are all subexpressions of%
~\eqref{gruntz_example_fn} and they all belong to the same comparability
class. This calculation can be done using SymPy as follows:

@@

In this example the result ($2+{1\over x}$) still depends on $x$, so the above procedure is
repeated until just a value independent of $x$ is obtained. This is the final
limit. In the above case the limit is $2$, as can be
verified by SymPy:\footnote{\label{suppnote:gruntz}To see the intermediate steps, discussed above, interested
readers can switch on debugging output by setting
the environment variable \texttt{SYMPY\_DEBUG=True}, before importing anything from
the SymPy namespace.}
